### 2015-09-24 README.Rmd
fix url in readme
updated readme

You need API keys for Encyclopedia of Life (EOL), the Universal Biological Indexer and Organizer (uBio), Tropicos, and Plantminer.

@@

	<td style="text-align:left;">uBio</td>
	<td style="text-align:left;"><code>ubio</code></td>
	<td style="text-align:left;"><a href="http://www.ubio.org/index.php?pagename=xml_services">link</a></td>
	<td style="text-align:left;"><a href="http://www.ubio.org/index.php?pagename=form">link</a></td>

@@

**: There are none! We suggest using `TPL` and `TPLck` functions in the [taxonstand package](http://cran.r-project.org/web/packages/Taxonstand/index.html). We provide two functions to get bullk data: `tpl_families` and `tpl_get`.

@@

```{r synonyms}
synonyms("Salmo friderici", db='ubio')
```

@@

```{r get_ids}
get_ids(names="Salvelinus fontinalis", db = c('ubio','ncbi'), verbose=FALSE)
```

>>>>

You need API keys for Encyclopedia of Life (EOL), Tropicos, and Plantminer.

@@

@@

**: There are none! We suggest using `TPL` and `TPLck` functions in the [taxonstand package](https://cran.rstudio.com/package=Taxonstand). We provide two functions to get bullk data: `tpl_families` and `tpl_get`.

@@

```{r synonyms}
synonyms("Acer drummondii", db="itis")
```

@@

```{r get_ids}
get_ids(names="Salvelinus fontinalis", db = c('itis', 'ncbi'), verbose=FALSE)
```
